Notes & Ideas

### 2018-11-30 course_notes.Rmd
update

**Marking Lab Reports (random thoughts on a different project)**

Text files for processed lab reports already are structured so we can use them like corpus files with inline meta-data. All lab reports have this as embedded metadata up front:

@@

Again, the main change we would need to make is to de-identify the student and TA. In theory I should be able to build some kind of direct replace functions for the TA-name and the Student-name.

>>>>

####Corpus Creation Using Student Lab Reports
(Random thoughts on a different project)

Text files for our processed lab reports already are structured so we can process them using Jerid's model for corpus files with inline meta-data.

All lab reports have these metadata embedded at the front end of the document:

@@

Again, the we would need to de-identify the student and TA using some kind of firewalled search/replace functions.
